\section{Statistical Analysis}\label{sec:stats}

The purpose of the statistical analyses was to detect the areas of activation associated with the noxious heat stimuli of 48$\degree$C. A statistical analysis was performed to show statistically significant activation within single heat runs, within single participants and within groups, respectively. General linear models (GLM) were used in all the analyses. A more detailed explanation of the GLM analysis can be found in the appendix \ref{back:sec:glm}. All analyses were performed on the data from standard preprocessing and FIX preprocessing, respectively. Both positive and negative activation were assessed for both preprocessing methods. Positive activation meant activation associated with the 48$\degree$C stimuli that was significantly higher than the baseline, where negative activation was activation significantly lower than the baseline.

\subsection{Within heat run analysis}
At a single heat run level the aim of the fMRI analysis is to analyze the time courses of every voxel to find out if the BOLD signal change in response to some perturbation. In this project, the aim of this analysis was to define brain responses to the 48$\degree$C heat stimuli delivered to the participants. GLM analysis was performed with the FSL tool FEAT (fMRIB’s Expert Analysis Tool) using a multivariate linear regression approach, as shown in \figref{fig:GLM} in \secref{back:sec:glm}. The BOLD signal time courses were set as the dependent variable, while the expected BOLD signal response for the 48$\degree$C stimuli, 47$\degree$C stimuli and the rating period made up the independent variables. As only the BOLD signal response of the 48$\degree$C stimuli was the signal of interest, the expected 47$\degree$C stimuli and the expected signal response to the rating periods were set as nuisance regressors. The nuisance regressors were used to account for the variability in the BOLD signal response of no interest. \\
The BOLD signal response is not instantaneous with the delivered stimulus, but delayed after the stimulus as a result of the hemodynamic response. It was therefore modeled by convoluting each regressor with a hemodynamic response function (HRF). The default shape of the HRF in FEAT is a  gamma function, which was also selected for this project. \\
The intercept and parameter estimates were calculated through FEAT by applying the ordinary least square method that minimizes distances between dependent and independent variables. The parameter estimates from the regressor of interest for each voxel were used to test the hypothesis about whether changes in brain activation was associated with the regressor of interest, i.e. 48$\degree$C stimuli. A t-test was applied to test if the parameter estimates were significantly different from the baseline. This resulted in a spatial map of significant activation for each heat run and participant, along with the within participant variance $\sigma_{W}^{2}$. \\
The parameter estimates explaining the activation were transformed into Z-statistics, from which a spatial map of activation explained in Z-scores was constructed. Furthermore a thresholding was applied, so that only clusters of activation above a Z-score of 2.3 was kept. This transformation was also applied on the parameter estimates obtained in the following two levels of analysis to construct the spatial maps of activation. 

\subsection{Within participant analysis}
To combine the results obtained for the individual heat runs within a participant, a fixed effect model was used. This fixed effect model applied a weighted average of the single heat run effect through a weighted linear regression approach. This was performed with the FIXED algorithm in FEAT. Here the weights were the inverse of the within participant variances $\sigma_{W}^{2}$ estimated for each of the three heat runs and the independent variable inputs were the parameter estimates acquired from the previous analysis. This analysis resulted in a new set of parameter and variance estimates, providing a single spatial map of significant activation for each participant for both preprocessing methods, respectively.

\subsection{Within group analysis}
The aim of the group-level analysis was to define significant activation across participants. This was done by using a mixed effect model, which treats the group as a random sample from a total population. This mixed effect model used the sum of the within participant variance $\sigma_{W}^{2}$ and the between participant variance $\sigma_{B}^{2}$ as weights in a weighted linear regression approach. The parameters estimated in the fixed effect model were used as the independent variable input. The within participant variances were estimated in the participant-level analysis, while $\sigma_{B}^{2}$ was estimated through the FLAME (FMRIB's Local Analysis of Mixed Effects) algorithm in the mixed effect model option in FEAT, which used an iterative process for the estimation. This was all done on a voxel level to provide more sensitive estimations.
To achieve a full spatial map of activation for all participants combined for both the standard preprocessed data and the FIX preprocessed data, respectively. A t-test was used to test if the estimated parameters differed significantly from the baseline for the data from each of the two preprocessing methods, respectively. 
To test the difference in activation in the data of the two preprocessing methods, the parameter estimates from the analysis of the standard preprocessed data and FIX preprocessed data were contrasted. This meant that when analyzing where activation was significantly higher in the FIX preprocessed data, the parameter estimates from the the standard preprocessed data were subtracted from the parameter estimates from the FIX preprocessed data. The new parameter estimates were tested against the baseline and transformed into Z-scores. The same process was performed to analyze where activation was higher for the standard preprocessed data compared to the FIX preprocessed data. This provided two spatial maps: one where the activation was significantly higher in the FIX preprocessed data compared to the standard preprocessed data, and one where the activation was significantly higher in the standard preprocessed data compared to the FIX preprocessed data.

To address the secondary research question it was analyzed if there was a relationship between the pain intensity ratings reported by the participants and the associated brain activation. To do this the mean pain intensity ratings for each participant were set as independent variables in a within group analysis, and the within participant brain activation for each participant were set the dependent variable. The regression model then estimated parameters for each voxel. If that parameter was not significantly higher than a Z-score of 2.3 when transformed into Z-statistics, no association between pain intensity rating and brain activation would be shown. 

\subsection{Activation common for test population}
Another way of comparing the two preprocessing methods is by looking at what activated brain regions different amounts of the test population have in common. To do this, first the spatial maps of all participants were merged across all volumes in the time course. Subsequently, the two merged spatial maps were binarized, leaving all activated voxels as 1 and all non-activated voxels as 0. Lastly, the mean within a voxel was calculated for the two spatial maps, respectively, leaving a single volume of mean activation. This made it possible to see activation common for all ranges between 0 and 100 percent of the test population. By superimposing the two spatial maps obtained, one for each preprocessing method, it would then be apparent how much activation each preprocessing method had removed and kept compared to each other for a certain amount of the test population. \cite{Coghill2003}
